---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# smoothAPC

<!-- badges: start -->
<!-- badges: end -->

The goal of smoothAPC is to model mortality rates as the sum of four components: a smooth bivariate function of age and time, smooth one-dimensional cohort effects, smooth one-dimensional period effects, and random errors. The model uses bivariate thin plate splines, bivariate lasso-type regularization, and allows for both period and cohort effects.

## Installation

You can install the **stable** version from
[CRAN](https://cran.r-project.org/package=smoothAPC):

```r
pak::pak("smoothAPC")
```

You can install the development version of smoothAPC from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("robjhyndman/smoothAPC")
```

## Example

```{r example}
library(smoothAPC)
m <- log(demography::fr.mort$rate$female[1:30, 150:160])
plot(m)
sm <- autoSmoothAPC(m)
plot(sm)
plot(sm, "period")
plot(sm, "cohort")
```
